Persistent somatic symptoms are key to individual illness perception at one year after COVID-19 in a cross-sectional analysis of a prospective cohort study

### 2023-03-06 paper/markdown/manuscript.Rmd
Change of the manuscript title

---
title: "Persistent somatic symptoms are key to individual illness perception at one year after COVID-19 in a cross-sectional prospective cohort study"
subtitle: "Illness perception one year after COVID-19"
date: "`r format(Sys.time(), '%Y-%m-%d')`"

>>>>

---
title: "Persistent somatic symptoms are key to individual illness perception at one year after COVID-19 in a cross-sectional analysis of a prospective cohort study"
subtitle: "Illness perception one year after COVID-19"
date: "`r format(Sys.time(), '%Y-%m-%d')`"

### 2023-03-06 paper/markdown/supplementary_material.Rmd
Change of the manuscript title

---
title: "Persistent somatic symptoms are key to individual illness perception at one year after COVID-19 in a cross-sectional prospective cohort study"
subtitle: "Supplementary Material"
author: "CovILD study team"
date: "`r format(Sys.time(), '%Y-%m-%d')`"

>>>>

---
title: "Persistent somatic symptoms are key to individual illness perception at one year after COVID-19 in a cross-sectional analysis of a prospective cohort study"
subtitle: "Supplementary Material"
author: "CovILD study team"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
